Avoiding tipping points in the management of ecological systems: a non-parametric Bayesian approach

### 2013-06-19 inst/doc/nonparametric-bayes.Rmd
update manuscript examples

```{r plot-options, echo=FALSE, cache=FALSE, include=FALSE}
options(xtable.print.comment=FALSE)
options(xtable.type = 'latex', table.placement="H")
opts_knit$set(progress = TRUE, verbose = TRUE)
opts_chunk$set(dev = 'Cairo_pdf', fig.width=5.5, fig.height=4,
 cache.path = 'cache/nonparametric-bayes/', cache=TRUE, external=TRUE)
opts_chunk$set(warning=FALSE, message=FALSE, comment=NA,
               tidy=FALSE, echo=FALSE)
```

@@

```{r mle, dependson="obs"}
```
```{r mle-output, dependson="mle"}
```

```{r gp-priors}
```
```{r gp, dependson=c("gp-priors", "obs")}
```
```{r gp_traces_densities, dependson="gp"}
```
```{r gp-output, dependson="gp"}
```

```{r jags-setup}
```
```{r common-priors}
```
```{r allen-model}
```
```{r allen-priors, dependson="common-priors"}
```
```{r allen-mcmc, dependson=c("allen-model", "allen-pars", "jags-setup"), results="hide"}
```
```{r allen-traces, dependson="allen-mcmc"}
```
```{r allen-posteriors, dependson=c("allen-traces", "allen-priors")}
```
```{r allen-output, dependson=c("posterior-mode", "allen-traces")}
```

```{r ricker-model}
```
```{r ricker-priors, dependson="common-priors"}
```
```{r ricker-mcmc, dependson="ricker-model", results="hide"}
```
```{r ricker-traces, dependson="ricker-mcmc"}
```
```{r ricker-posteriors, dependson=c("ricker-traces", "ricker-priors")}
```
```{r ricker-output, dependson=c("posterior-mode", "ricker-traces")}
```

```{r myers-model}
```
```{r myers-priors}
```
```{r myers-mcmc, dependson="myers-model", results="hide"}
```
```{r myers-traces, dependson="myers-mcmc"}
```
```{r myers-posteriors, dependson="myers-traces"}
```
```{r myers-output, dependson=c("posterior-mode", "myers-traces")}
```

@@

```{r profits, dependson="sims", results="hide"}
```
```{r deviances, dependson=c("posterior-mode", "myers-output", "ricker-output", "allen-output", "gp-output", "mle-output"), results="hide"}
```

>>>>

```{r plot-options, echo=FALSE, cache=FALSE, include=FALSE}
options(xtable.print.comment=FALSE)
options(xtable.type = 'latex', table.placement="H")
opts_knit$set(progress = TRUE, verbose = TRUE)
opts_chunk$set(dev = c('pdf', 'png'), fig.width=5.5, fig.height=4,
 cache.path = 'cache/nonparametric-bayes/', cache=TRUE, external=TRUE)
opts_chunk$set(warning=FALSE, message=FALSE, comment=NA,
               tidy=FALSE)
toggle = "markup" # "hide" 
```

@@

```{r mle, dependson="obs"}
```
```{r mle-output, dependson="mle", results=toggle}
```

```{r gp-priors}
```
```{r gp, dependson=c("gp-priors", "obs")}
```
```{r gp_traces_densities, dependson="gp"}
```
```{r gp-output, dependson="gp", results=toggle}
```

```{r jags-setup}
```
```{r common-priors}
```
```{r allen-model}
```
```{r allen-priors, dependson="common-priors"}
```
```{r allen-mcmc, dependson=c("allen-model", "allen-pars", "jags-setup"), results=toggle}
```
```{r allen-traces, dependson="allen-mcmc"}
```
```{r allen-posteriors, dependson=c("allen-traces", "allen-priors")}
```
```{r allen-output, dependson=c("posterior-mode", "allen-traces"), results=toggle}
```

```{r ricker-model}
```
```{r ricker-priors, dependson="common-priors"}
```
```{r ricker-mcmc, dependson="ricker-model", results=toggle}
```
```{r ricker-traces, dependson="ricker-mcmc"}
```
```{r ricker-posteriors, dependson=c("ricker-traces", "ricker-priors")}
```
```{r ricker-output, dependson=c("posterior-mode", "ricker-traces"), results=toggle}
```

```{r myers-model}
```
```{r myers-priors}
```
```{r myers-mcmc, dependson="myers-model", results=toggle}
```
```{r myers-traces, dependson="myers-mcmc"}
```
```{r myers-posteriors, dependson="myers-traces"}
```
```{r myers-output, dependson=c("posterior-mode", "myers-traces"), results=toggle}
```

@@

```{r profits, dependson="sims", results=toggle}
```
```{r deviances, dependson=c("posterior-mode", "myers-output", "ricker-output", "allen-output", "gp-output", "mle-output"), results=toggle}
```
